\thetitle

### 2020-11-21 writing/discussion.tex
revision of discussion

There are a number of threats to the

@@

Surprisingly, Transient blames an empty set of boundaries in 967 cases.
Such cases should never occur, at least in theory, because an empty set
 means the value has never crossed a boundary---if the value is indeed defined
 in the current module, then we have typed code blaming itself for a typed
 value; thus, the type checker must be unsound.
After careful investigation of these empty blame cases, we found no soundness
 bugs in Typed Racket.
Instead, we found scenarios in which Transient lost track of the proper
 boundaries.
These scenarios suggest ways to improve the blame algorithm from~\citet{vss-popl-2017}:
\begin{itemize}
  \item
    Entries in a blame map must point to several parent entries.
    For example, if the function \texttt{f} receives bad input in the call
    \texttt{(filter f xs)}, then blame should point to both \texttt{filter}
    and the \texttt{xs} list.
  \item
    The construction of blame map entries must be guided by type-like specifications
     instead of relying on syntax.
    Aliasing the built-in \texttt{filter} function should not change the shape
     of the blame map.
  \item
    The initial blame map must reflect the initial type environment.
    For instance, Typed Racket trusts that untyped core-library functions, such as \texttt{filter},
     behave correctly; such assumptions should appear in the blame map.
\end{itemize}
\noindent{}Despite these known limitations, we conjecture that these improvements
 to Transient blame-tracking will not affect our overall conclusions.

>>>>

There are a number of threats to the validity of our conclusions that we
describe in the previous section our attempts to mitigate: (i) the
representativeness of benchmarks; (ii) the relation between mutations and
real programming mistakes; (iii) the definition of interesting debugging
scenarios; and (iv) our approach to sampling scenarios. In the remainder
of this section, we discuss extensively two additional threats.

@@

As we discuss in section~\ref{sec:results}, surprisingly Transient blames
an empty set of boundaries in 967 scenarios.
Such cases should never occur, at least in theory, because an empty set
 means the value has never crossed a boundary---if the value is indeed defined
 in the current module, then we have typed code blaming itself for a typed
 value as all the checks are inlined in typed code. Thus, the type checker must be unsound.
After careful investigation of these empty blame cases, we found no soundness
 bugs in Transient Typed Racket.
Instead, we found scenarios in which Transient lost track of the proper
 boundaries.
These scenarios suggest ways to improve~\citet{vss-popl-2017}'s blame
algorithm:
\begin{itemize}
  \item
    Entries in a blame map must point to several parent entries.
    For example, if the function \texttt{f} receives bad input in the call
    \texttt{(filter f xs)}, then blame should point to both \texttt{filter}
    and the \texttt{xs} list.
  \item
    The construction of blame map entries must be guided by type-like specifications
     instead of relying on syntax.
    Aliasing the built-in \texttt{filter} function should not change the shape
     of the blame map.
  \item
    The initial blame map must reflect the initial type environment.
    For instance, Typed Racket trusts that untyped core-library functions, such as \texttt{filter},
     behave correctly; such assumptions should appear in the blame map.
\end{itemize}
\noindent{}Despite these known limitations, based on the relatively small
number of debugging failures, we conjecture that these improvements
 to Transient blame-tracking do not affect our overall conclusions.
